Water Management

### 2020-01-23 Paper/paper.tex
temporary changes
plot graphs using matlab and include them in latex

	\section{Main Part}
	\subsection{bla}
	\begin{figure}[ht] % TODO remove example
		\includegraphics[width=1\textwidth]{figures/example.png}
		\caption{Example Image}
		\label{fig:example-pic}
	\end{figure}
	\blindtext
	\begin{figure}[ht] % TODO remove example
		\begin{longtable}{|p{2,5cm}|p{2,5cm}|p{2,5cm}|p{3cm}|p{3cm}|}
			\hline
			&\multicolumn{4}{c|}{\textbf{Klasse}} \\
			\hline
			& \textbf{S0} & \textbf{S1} & \textbf{S2} & \textbf{S3} \\
			\hline
			\textbf{lorem} & ipsum & ipsum & ipsum & ipsum \\
			\hline
		\end{longtable}
		\label{fig:example-figure}
		\caption{Example Table}
	\end{figure}
	\blindtext
	\blindtext
	\blindtext

@@

	\section{Conclusion}
	This chapter will discuss the outcomes and results of the implemented functionality in MATLAB.
	The discussion will be started on the basic questions asked by the project description.
	Furthermore we made several modifications to the task which will be discussed additionally.
	All results will be visualized by plots made within our simulation in MATLAB.
	\subsection{Optimal irrigation policy}
	\subsection{Steady State}
	\subsection{Steady State Probability}
	\subsection{Effect of Changed Discount Factors to Optimal Irrigation Policy}
	\subsection{Changed Volatility of Rainfalls}

>>>>

	\section{Main Part}
	\subsection{Theory}
	(Für die Präsentation)

%	\begin{equation}
%	V_t =  max\{u_{farmer}(irrigation_t) + u_{recreationalUser}(irrigation_t, waterLevel_t) \\
%		
%	+ 	\beta*(u_{farmer}(irrigation_{t-1}) + u_{recreationalUser}(irrigation_{t-1}, waterLevel_{t-1})\}
%	\end{equation}

	\blindtext
	\begin{figure}[ht]
		\begin{longtable}{|p{2,5cm}|p{2,5cm}|p{2,5cm}|p{3cm}|p{3cm}|}
			\hline
			&\multicolumn{4}{c|}{\textbf{Klasse}} \\
			\hline
			& \textbf{S0} & \textbf{S1} & \textbf{S2} & \textbf{S3} \\
			\hline
			\textbf{lorem} & ipsum & ipsum & ipsum & ipsum \\
			\hline
		\end{longtable}
		\label{fig:example-figure}
		\caption{Example Table}
	\end{figure}
	\blindtext
	\blindtext
	\blindtext

@@

	\section{Conclusion}
	This chapter will discuss the outcomes and results of the implemented functionality in MATLAB.
	The discussion will be started on the basic questions asked by the project description.
	Furthermore we made several modifications to the task which will be discussed additionally.
	All results will be visualized by plots made within our simulation in MATLAB.
	\subsection{Optimal irrigation policy}
	When questioning what the optimal irrigation policy is, the first question to be asked is how the aggregated value function of both recreational users and farmers looks like.
	The value function as posed in % TODO put links to theory here
	contains the maximum possible usage that can be gained by irrigating a specific amount of water under a given water level. 
	\ref{fig:value-function} show the value function calculated for all possible water levels between the allowed boundaries of 0 and 7.
	\begin{figure}[ht]
		\includegraphics{figures/value_function.eps}
		\caption{Value Function}
		\label{fig:value-function}
	\end{figure}
	\begin{figure}[ht]
		\includegraphics{figures/OptimalIrrigationPolicy.eps}
		\caption{Optimal Irrigation Policy}
		\label{fig:optimal-irrigation-policy}
	\end{figure}
	\subsection{Steady State}
	\begin{figure}[ht]
		\includegraphics{figures/steadyState.eps}
		\caption{Exemplary Calculation of the Steady State}
		\label{fig:steadyState}
	\end{figure}
	\subsection{Steady State Probability}
	\begin{figure}[ht]
		\includegraphics{figures/steadyStateMonteCarlo.eps}
		\caption{Steady State Probability}
		\label{fig:steadyStateMonteCarlo}
	\end{figure}
	\subsection{Effect of Changed Discount Factors to Optimal Irrigation Policy}
	\subsection{Changed Volatility of Rainfalls}
